SST_patterns

### 2019-08-21 SST_patterns.Rmd
update

# Are the same upwelling signals present at different distances from the coastline and through the different datasets

>>>>

# Are the same upwelling signals present at different distances from the coastline and throughout the different datasets

```{r}
knitr::opts_chunk$set(
  comment = "R>",
  warning = FALSE,
  message = FALSE 
)

library(tidyverse)
# library(plyr)
library(lubridate)
library(ggpubr)
library(zoo)
library(FNN)
library(forecast)
library(astrochron)
library(WaveletComp)
library(data.table)
library(heatwaveR)
library(viridis)
library(ggrepel)
library(maptools)
library(sp)
library(geosphere)
library(PBSmapping)
library(scales)
library(grid)
library(gridExtra)
library(circular)
library(fossil)
library(mapproj)
library(ncdf4)
library(stringr)
library(doMC); doMC::registerDoMC(cores = 4)
library(fasttime)
library(xtable)
```

# Loading in all the data created using the code bellow

```{r}
load("Data/site_list_sub.Rdata")
load("Data/SACTN_US.RData")
load("Data/site_pixels.RData")
load("Data/OISST.RData")
load("Data/CMC.RData")
load("Data/MUR.RData")
```

```{r}
# SACTN_US <- SACTN_US %>% 
#   dplyr::rename(in_situ_temp = temp)
# 
# # Visualising the data
# temp_plot <- function(df){
#   plot <- ggplot(data = df, aes(x = date, y = in_situ_temp, colour = site)) +
#     geom_line(aes(group = site)) +
#     labs(x = "", y = "Temperature (°C)") +
#     theme(axis.text.x = element_text(angle = 45)) +
#     theme(legend.position = "top")
# }
# 
# SACTN_plot <- temp_plot(df = SACTN_US)
# SACTN_plot
```

# Loading MUR data

```{r}
# MUR_Lamberts_Bay <- read_csv("Data/MUR/MUR_Lamberts Bay_SST_timeseries_5nearest.csv")
# MUR_Port_Nolloth <- read_csv("Data/MUR/MUR_Port Nolloth_SST_timeseries_5nearest.csv")
# MUR_Saldanha_Bay <- read_csv("Data/MUR/MUR_Saldanha Bay_SST_timeseries_5nearest.csv")
# MUR_Sea_Point <- read_csv("Data/MUR/MUR_Sea Point_SST_timeseries_5nearest.csv")
# MUR_Hout_Bay <- read_csv("Data/MUR/MUR_Hout Bay_SST_timeseries_5nearest.csv")
# 
# MUR_SST <- rbind(MUR_Lamberts_Bay,MUR_Hout_Bay, MUR_Port_Nolloth,MUR_Saldanha_Bay, MUR_Sea_Point) %>%
#   dplyr::rename(site = station)
# 
# MUR_SST$date <- (ymd(MUR_SST$date))
# MUR_SST <- MUR_SST %>% 
#   dplyr::rename(temp = nearest1) %>% 
#   drop_na()
# 
# match_func <- function(df){
#   match <- SACTN_US  %>%  
#   left_join(df, by = c("site", "date")) %>% 
#   na.trim()
#   return(match)
# }
# 
# MUR <- match_func(df = MUR_SST) %>%
#   drop_na()
# 
# # save(MUR, file = "Data/MUR.RData")
# 
# match_plot <- function(df){
#   plot1 <- df %>% 
# ggplot(aes(x = date, y = temp)) +
#   geom_hline(aes(yintercept = mean(temp)), colour = "salmon") +
#   geom_line() +
#   facet_wrap(~ site, nrow = 2) +
#   theme_bw()
#   return(plot1)
# }
# 
# MUR_plot <- match_plot(df = MUR)
# MUR_plot
```

# CMC data

```{r}
# CMC_Sea_Point <- read_csv("Data/CMC/Sea Point_SST_timeseries_5nearest.csv")
# CMC_Lamberts_Bay <- read_csv("Data/CMC/Lamberts Bay_SST_timeseries_5nearest.csv")
# CMC_Port_Nolloth <- read_csv("Data/CMC/Port Nolloth_SST_timeseries_5nearest.csv")
# CMC_Saldanha_Bay <- read_csv("Data/CMC/Saldanha Bay_SST_timeseries_5nearest.csv")
# CMC_Hout_Bay <- read_csv("Data/CMC/Hout Bay_SST_timeseries_5nearest.csv")
# 
# CMC_SST <- rbind(CMC_Lamberts_Bay,CMC_Hout_Bay, CMC_Port_Nolloth, CMC_Saldanha_Bay, CMC_Sea_Point) %>%
#   dplyr::rename(site = station)
# 
# CMC_SST$date <- (ymd(CMC_SST$date))
# CMC_SST <- CMC_SST %>% 
#   dplyr::rename(temp = nearest1) %>% 
#   drop_na()
# 
# match_func <- function(df){
#   match <- SACTN_US  %>%  
#   left_join(df, by = c("site", "date")) %>% 
#   na.trim()
#   return(match)
# }
# 
# CMC <- match_func(df = CMC_SST) %>%
#   drop_na()
# 
# # save(CMC, file = "Data/CMC.RData")
# 
# CMC_plot <- match_plot(df = CMC)
# CMC_plot
```

# Loading the OISST

```{r}
# OISSTDir <- "~/Documents/Masters_2019/Data_SST"
# OISST <- fread(paste0(OISSTDir, "/csvavhrr-only-v2-19810901-20180630.csv"),
#             col.names = c("lon", "lat", "temp", "date"))
# 
# # Visualise the data
# # To explore the data I visualise the min temperatures along the South african coastline.
# 
# OISST %>%
#   filter(date == min(date)) %>%
#   ggplot(aes(x = lon, y = lat)) +
#   geom_raster(aes(fill = temp))
# 
# load("Data/site_list_sub.Rdata") # Loading the SACTN_overlap dataset which allows me to match it to the OISST data 
# 
# unique_pixel <- OISST %>%
#   select(lon, lat) %>%
#   unique()
# 
# # Select nearest 1 pixels (k = 1)
# # Here I use knnx to find the closes 1 pixels to the insitu sites
# match_index <- knnx.index(data = as.matrix(unique_pixel[,1:2]),
#                       query = as.matrix(site_list_sub[,5:6]), k = 1)
# 
# pixel_match <- unique_pixel[match_index,] %>%
#   unite(col = combi, lon, lat, sep = "/", remove = F) %>%
#   mutate(site = site_list_sub$site)
# 
# # Subsetting the OISST data to match the upwelling sites within the in situ collected temperature data
# OISST_match <- OISST %>%
#   unite(col = combi, lon, lat, sep = "/", remove = F) %>%
#   filter(combi %in% pixel_match$combi)
# # save(OISST_match, file = "Data/OISST_match.RData")
# 
# OISST_sites <- OISST_match %>%
#   left_join(pixel_match, by = c("combi", "lon", "lat")) #%>%
#   #dplyr::rename(temp_OISST =temp)
# 
# OISST_sites <- OISST_sites %>% 
#   dplyr::mutate(date = as.Date(date)) %>% 
#   drop_na()
# # save(OISST_sites, file = "Data/OISST_sites.RData")
# 
# ## Matching the Insitu data with the OISST SST data
# OISST <- match_func(df = OISST_sites)
# # save(OISST, file = "Data/OISST.RData")
```

Different distances from the coastline

```{r}
# load("Data/site_list_sub.Rdata")
# # xtable(site_list_sub, auto = TRUE)
# west <- site_list_sub
# west$coast <- "west" # Chnages wc to west
# 
# load("Data/africa_coast.RData")
# 
# ## Downloading the bathy data from NOAA
# # Download mid-res bathymetry data
# # sa_lat <- c(-38, -24.5); sa_lon <- c(11.5, 35.5)
# # sa_bathy <- as.xyz(getNOAA.bathy(lon1 = sa_lon[1], lon2 = sa_lon[2], lat1 = sa_lat[1], lat2 = sa_lat[2], resolution = 4))
# # colnames(sa_bathy) <- c("lon", "lat", "depth")
# # sa_bathy <- sa_bathy[sa_bathy$depth <= 0,]
# # save(sa_bathy, file = "Data_P1/bathy/sa_bathy.RData")
# 
# # Loading in the newly downloaded bathymetry data
# load("Data/bathy/sa_bathy.RData")
# 
# # This function takes one site (e.g. one set of lon/lats) and calculates a shore normal transect
# shore.normal.transect <- function(site, width = 2){
#   # Find the site on the coastline and it's nearest neighbour points
#   coords <- data.frame(lon = site$lon, lat = site$lat)
#   coords2 <- knnx.index(africa_coast[,1:2], as.matrix(coords), k = 1)
#   coords3 <- data.frame(site = site$site, africa_coast[c(coords2-width, coords2+width),]) 
#   coords3 <- coords3[2:1,1:3]
#   # Define the shore normal transect bearing
#   heading <- earth.bear(coords3[1,2], coords3[1,3], coords3[2,2], coords3[2,3]) + 90
#   if(heading >= 360){
#     heading <- heading-360
#   } else {
#     heading <- heading
#   }
#   heading2 <- data.frame(site = site$site, lon = site$lon, lat = site$lat, heading)
#   return(heading2)
# }
# 
# # Creating the transects
# site_transects <- data.frame()
# for(i in 1:length(west$site)){
#  site <- west[i,]
#  site_transect <- shore.normal.transect(site, 2)
#  site_transects <- rbind(site_transects, site_transect)
# }
# 
# # Manually correcting Sea Point and Kommetjie
# site_transects$heading[4:5] <- 290 
# # save(site_transects, file = "Data/site_transects.RData")
# load("Data/site_transects.RData")
# 
# # This function takes one site (e.g. one set of lon/lats) and calculates a shore normal transect
# # It then extracts a lat/ lon point every X kilometres until reaching a specified isobath
# 
# transect.pixel <- function(site, distances){
#   # Extract coordinates
#   coords <- data.frame(lon = site$lon, lat = site$lat)
#   # Find lon/ lats every X metres 
#   pixels <- data.frame()
#   # deep <- 999
#   # distance_multiplier <- 1
#   # while(deep > isobath){
#   for(i in 1:length(distances)){
#     coords2 <- as.data.frame(destPoint(p = coords, b = site$heading, d = distances[i]))
#     sitesIdx <- knnx.index(sa_bathy[,1:2], as.matrix(coords2), k = 1)
#     bathy2 <- sa_bathy[sitesIdx,]
#     bathy2 <- bathy2[complete.cases(bathy2$depth),]
#     bathy3 <- data.frame(site = site$site, lon = bathy2$lon, lat = bathy2$lat, 
#                          heading = site$heading, 
#                          distance = distances[i])
#     pixels <- rbind(pixels, bathy3)
#     coords <- coords2
#   }
#   if(nrow(pixels) < 1){
#     pixels <- data.frame(site, depth = NA)
#   }else{
#     pixels <- pixels
#   }
#   return(pixels)
# }
# 
# # Pixel points
# site_pixels <- data.frame()
# for(i in 1:length(west$site)){
#   site <- site_transects[i,]
#   site_pixel <- transect.pixel(site, c(10000, 20000, 30000, 40000, 50000)) # RWS: fixed error
#   site_pixels <- rbind(site_pixels, site_pixel)
# }
# 
# # Bounding box
#   # Only one is made in order to know how large the the geom_point() squares should be made to match
# bbox <- data.frame(xmin = destPoint(p = site_pixels[1,2:3], b = 270, d = 12500)[1],
#                    xmax = destPoint(p = site_pixels[1,2:3], b = 90, d = 12500)[1],
#                    ymin = destPoint(p = site_pixels[1,2:3], b = 180, d = 12500)[2],
#                    ymax = destPoint(p = site_pixels[1,2:3], b = 0, d = 12500)[2])
# 
# # Determining the temperature at the various distances from the coast
# 
# # save(site_pixels, file = "Data/site_pixels.RData")
# load("Data/site_pixels.RData")
```

# Using the upwelling metrics created in `upwell.IDX.Rmd` Identify when upwelling occurs at the particular site. 
# Is this upwelling event seen throughout the different distances from the coastline
# Using CMC, MUR, OISST and SACTN_US to determine wether the upwelling events detected is present in each of the datasets
